\documentclass{resumestyle}
\usepackage[english]{babel}

\begin{document}
\setstretch{1.05}% line space
\large% font size  

% --------
% HEADER
% --------
\part{Araf Al-Jami}

% -------------------
% EDUCATION
% -------------------
\section{Education}%

% \begin{spacing}{1.05}
\textbf{Leading University, Sylhet, Bangladesh}\\% college
\textit{Bachelor of Science}\\% degree name
{09/2014 - 12/2018}\\% degree duration
Major : Computer Science and Engineering\\% degree
CGPA: 3.34 / 4.00% GPA
% \end{spacing}

% -------------------
% WORK EXPERIENCE
% -------------------
\section{Work Experience}%
    \worksubsection%
        {Software Engineer}%
        {Agoda}%
        {Dhaka, Bangladesh | 11/2021 - 12/2021 (Contract via Accurate Consultant Limited)}\\%
        {Bangkok, Thailand | 01/2022 - Present (Fulltime)}%
    
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item Developed RESTful APIs using C\# and ASP.NET Core Technologies.%
        \item Wrote stored procedure for Microsoft SQL Server.%
        \item Developed worker service using Scala and C\#.%
    \end{itemize}%

    \vspace{4pt}%

    \worksubsection%
        {Software Engineer}%
        {Shohoj Limited}%
        {Dhaka, Bangladesh | 02/2020 - 10/2021}%
    
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item Developed RESTful APIs in an event-driven microservice architecture.%
        \item Improved the performance of nearest provider search upto 33\% by refining the algorithm and data store.
        \item Worked on a service to provide Identity Access Management service for millions of users.%
        \item Architected a User Access Management system that consolidated user management for six different verticals into a single system.%
        \item Developed tools to migrate millions of users from different user stores to a single consolidated user store.%
        \item Implemented a service to aggregate location history data in a friendly format for analytics using RabbitMQ to aggregate the history in an asynchronous process.%
        \item Wrote scripts/tools to load test services ensuring the desired performance is achieved.%
        \item Followed Test Driven Development methodology to write robust, adaptable code.%
    \end{itemize}%

    \vspace{4pt}%


    \worksubsection%
        {Software Engineer}%
        {Secure Link Services BD Ltd (SELISE)}%
        {Dhaka, Bangladesh | 11/2018 - 01/2020}%
    
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item Developed full stack web applications fulfilling business requirements using Angular and .NET Core Technologies.%
        \item Worked on multiple projects and implemented business requirements for Selise Auditing and Certification Platform.%
    \end{itemize}%

    \vspace{0pt}%

% -------------------
% AREAS OF EXPERTISE
% -------------------
% \vspace{4pt}\\
\section{Technical Skills}%
\tag{C/C\scalebox{1.0}{++}}\enspace%
\tag{Python}\enspace%
\tag{JavaScript}\enspace%
\tag{.NET}\thinspace\thinspace%
\tag{C\#}\vspace{4pt}\\%
\tag{TypeScript}\enspace%
\tag{Linux}\enspace%
\tag{Git}\enspace%
\tag{Docker}\enspace%
\tag{Angular}\vspace{4pt}\\%
\tag{Nodejs}\thinspace\thinspace%
\tag{Express}\thinspace\thinspace%
\tag{SQL}\enspace%
\tag{NoSQL}\enspace%
\tag{Nginx}\vspace{4pt}\\%
\tag{REST}\thinspace\thinspace%
\tag{Redis}\thinspace\thinspace%
\tag{RabbitMQ}\thinspace\thinspace%
\tag{MongoDB}\thinspace\thinspace%
\tag{Mqtt}\vspace{4pt}\\%
\tag{Scala}%


% -------------------
% PERSONAL PROJECTS
% -------------------
\section{Personal Projects}%
    
    \projectsubsection%
        {Coder Ranklist}%
        {Visualization \hfill \textit{\href{https://www.lus.ac.bd/cp__trashed/ranklist/}{\textcolor{link}{link}}}}%
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item Generated programming profile for easier evaluations of overall performance and exposed the data via RESTful APIs using Node.js, MongoDB, Redis and Heroku.
    \end{itemize}%

    \projectsubsection%
        {Project Renegade}%
        {Video Game \hfill
        \textit{\href{https://github.com/CLown1331/Unity-FPS/releases/tag/1.0.0/}{\textcolor{link}{link}}}}%
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item An FPS game on Android Platform. Developed as University Third year final project. Technologies used: Unity3d, C\#, Blender.
        \item Led the development team, executed the development process, helped with task distribution.
        \item Developed the Gameplay system, UI System, AI System.
    \end{itemize}%    

\vspace{8pt}

% -------------------
% AWARDS & ACHIEVEMENTS
% -------------------
\section{AWARDS \& ACHIEVEMENTS}%

    \worksubsection%
        {Competitive Programming Contests}%
        {September 2014 - Present}%
        {}%
    
    \begin{itemize}[labelsep=4pt,leftmargin=*,topsep=5pt,partopsep=0pt,itemsep=1pt]%
        \item 10th place (4th place University wise) out of 150 teams at IUBAT ACM NCPC 2018. {\href{https://araf.aljami.me/assets/pdf/2019-Bangladesh%20IUBAT%20NCPC-PLACE.pdf}{[link]}}
        \item 16th place at ACPC ICPC Dhaka Regional 2017. {\href{https://araf.aljami.me/assets/pdf/2018-Asia%20Dhaka%202017-PLACE.pdf}{[link]}}
        \item Active participant in online coding challenges on sites such as {\href{https://www.topcoder.com/members/CLown1331/}{TopCoder}}, {\href{http://codeforces.com/profile/CLown1331}{Codeforces}}.
        \item Achieved Maximum Rating of 1982 (top 4\%) in Codeforces. Handle: {\href{http://codeforces.com/profile/CLown1331}{CLown1331}}. 
        \item Achieved Maximum Rating of 1469 (Division 1) in TopCoder. Handle: {\href{https://www.topcoder.com/members/CLown1331/}{CLown1331}}.
    \end{itemize}%


\end{document}