\documentclass{resume}

\usepackage{hyperref}
\hypersetup{hidelinks}
\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Araf Al-Jami} 
\address{\href{mailto:arafaljami1331@gmail.com}{arafaljami1331@gmail.com} \\ \href{https://araf.aljami.me/}{araf.aljami.me} \\ {}{+8801755045141} \\ {}{Dhaka, Bangladesh}}

\begin{document}

%----------------------------------------------------------------------------------------
%       Summary
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
Around 2 years of working experience as a software engineer, with a strong pursuit of problem solving.
Hands on experience in building enterprise applications and maintaining best practices with OOD.
Followed SOLID principles and design patterns to write clean, maintainable and adaptive code.
\end{rSection}

%----------------------------------------------------------------------------------------
%       Skills
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
{\bf Languages:} C\#, Typescript, Javascript, C/C++\\
{\bf Specialties:} .NET, .NET Core, Node js, Express, Web API, Git, IdentityServer4, Agile, Angular\\
{\bf Database and messaging:} MongoDB, EF Core, MySQL, MassTransit, RabbitMQ, Mqtt, Azure Service Bus.
\end{rSection}

%----------------------------------------------------------------------------------------
%       EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Leading University, Sylhet} \hfill {\em September 2014 - April 2019}
\\ Bachelor of Science in Computer Science and Engineering
\end{rSection}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Shohoj Limited, Dhaka}{Feb 2020 - Present}{Software Engineer, Backend}{}

\item Refined the \textbf{Nearest provider search}, improving the performance up to \textbf{3x} times.
\item Developed a service to provide, \textbf{Identity Access Management} service for \textbf{1+ million  users}.
\item Developed tools to migrate \textbf{1+ million users}, from \textbf{12} different user store to \textbf{1} single consolidated user store.
\item Designed and developed, \textbf{User Access Management} system which consolidated user management for \textbf{6} different verticals to \textbf{1} single system.
\item Implemented a service, to aggregate location history data in friendly format for data science team.
\end{rSubsection}

\begin{rSubsection}{Leading University, Sylhet}{Jul 2020 - Present}{Competitive Programming Trainer}{}
\item Arranged and taken class on competitive programming topics, data structures, algorithms.
\item Arranged practice contest for students.
\end{rSubsection}

\begin{rSubsection}{SELISE rockin' software, Dhaka}{Nov 2018 - Jan 2020}{Software Engineer}{}
\item Used Angular, AngularJS to develop Single Page Applications
\item Used Dotnet Core technologies to develop REST API.
\item Worked on multiple projects and implemented business requirements for Selise Auditing and Certification Platform.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%       Awards & Achievements
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Achievements} 

\begin{rSubsection}{Onsite Competitive Programming Contests}{\em September 2014 - Present}{}{}{}
\item \href{https://icpc.baylor.edu/ICPCID/DII3NHEO8O8I}{\textbf{$10^{th}$} place (\textbf{$4^{th}$} place University wise) out of \textbf{150} teams, at IUBAT ACM NCPC 2018}. \href{https://icpc.baylor.edu/ICPCID/DII3NHEO8O8I}{[link]}
\item \textbf{$16^{th}$} place \textbf(\textbf{$8^{th}$} place University wise) out of \textbf{120} teams, at MIST IUPC 2019
\end{rSubsection}

\begin{rSubsection}{Online Competitive Programming Contests}{\em September 2014 - Present}{}{}{}
\item Active participant in online coding challenges on sites such as \textbf{TopCoder}, \textbf{Codeforces}.
\item Achieved Maximum Rating of \textbf{1982 (top 4\%)} in \textbf{Codeforces}. \textbf{Handle:} \textbf{\href{http://codeforces.com/profile/CLown1331}{CLown1331}}. \href{http://codeforces.com/profile/CLown1331}{[link]}
\item Achieved Maximum Rating of \textbf{1469 (Division 1)} in \textbf{TopCoder}. \textbf{Handle:} \textbf{\href{https://www.topcoder.com/members/CLown1331/}{CLown1331}}. \href{https://www.topcoder.com/members/CLown1331/}{[link]}
\item \href{https://www.stopstalk.com/user/profile/clown1331}{Solved around 2800 problems in various online judges.} \href{https://www.stopstalk.com/user/profile/clown1331}{[link]}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%       Project
%----------------------------------------------------------------------------------------

\end{document}
